Features of Accretion Phase Gravitational Wave Emission from Two-dimensional Rotating Core-Collapse Supernovae

### 2019-04-17 ms.tex
One or two word changes

 \begin{figure*}[htp]
  \centering     %%% not \center
  \includegraphics[width=\textwidth]{tdwf_region_20.pdf}
  \caption{Time domain waveforms for the 20 $M_\odot$ progenitor.  Each panel corresponds to the region from which the GWs are emitted.  The large contribution in the top panel indicates the main source of GWs during the accretion phase is from the vibrating PNS.  The middle panel displays the inhibited convective signal $\sim 50-100 $ ms post bounce that is characteristic of this quiescent phase.}
  \label{fig:region}
\end{figure*}

@@

    \software{\\\href{http://flash.uchicago.edu/site/}{FLASH} \citep{fryxell:2000,fryxell:2010},\\ \href{https://matplotlib.org/}{Matplotlib} \citep{hunter:2007},\\ \href{http://www.numpy.org/}{NumPy} \citep{vanderwalt:2011},\\ \href{https://www.scipy.org/}{SciPy} \citep{jones:2001}}

>>>>

 \begin{figure*}[htp]
  \centering     %%% not \center
  \includegraphics[width=\textwidth]{tdwf_region_20.pdf}
  \caption{Time domain waveforms for the 20 $M_\odot$ progenitor.  Each panel corresponds to the region from which the GWs are emitted.  The large contribution in the top panel indicates the main source of GWs during the accretion phase is from the vibrating PNS.  The lower panel displays the inhibited convective signal $\sim 50-100 $ ms post bounce that is characteristic of this quiescent phase.}
  \label{fig:region}
\end{figure*}

@@

    \software{\\\href{http://flash.uchicago.edu/site/}{FLASH} \citep{fryxell:2000,fryxell:2010},\\ \href{https://matplotlib.org/}{Matplotlib} \citep{hunter:2007},\\
    \href{http://www.nulib.org}{NuLib}
    \citep{oconnor:2015},\\
    \href{http://www.numpy.org/}{NumPy} \citep{vanderwalt:2011},\\ \href{https://www.scipy.org/}{SciPy} \citep{jones:2001}}
